---
title: 'Exercise #1'
output: 
  html_document:
    toc: true
    toc_float: true
    df_print: paged
    code_download: true
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

```{r libraries}
library(tidyverse)         # for graphing and data cleaning
```

```{r data}
data(mpg) # this dataset is part of an R package
```

Just like I did above, at the top of the file, put three R code chunks. The first controls options. Right now I have it commented out (a `#` sign in front), but you should uncomment (remove the `#`) when your document is complete so you don't see messages and warnings. The second loads libraries. It is nice to give a brief description of what the library does to remind yourself why you are loading it. The third loads any data used in the document.

The yaml section of the document (the part at the very top, between the set of three dashes) is EXTREMELY picky but it also gives you a way to customize your document. If you want to learn more about changing this section see [section 3.1.4](https://bookdown.org/yihui/rmarkdown/html-document.html#appearance-and-style) of the *R Markdown: The Definitive Guide* by Yihui Xie, J. J. Allaire, and Garrett Grolemund.

Use headings and subheadings to number your problems, like I've done below.  Leave a space before and after each R code chunk, so code, comments, and output print out nicely. Write in complete sentences to answer your questions. Your comments should clearly reference the R code and output that you include. Do not include R code and output that you don't reference.

## Exercise 1: Setting up Git and GitHub in RStudio.

Task: Post a link to your GitHub repository.   <br>
A Link to my GitHub repository for STAT494 can be found <a href = "https://github.com/EmmanuelUgo/stat494"> here </a> 


## Exercise 2: Creating a website

Task: Include a link to your website below. <br> 
A link to my website can be found <a href = "" > here </a>
 
### a. 

### b. 

...
